03-methods

### 2024-05-23 03-methods.qmd
revisada introduccion y antecedentes, temas menores formato
corrección methods

---
author: "Equipo Edumer"
format: pdf
editor: visual
---

## Data, variables and method

### Data

The main data source corresponds to the First Study of Civic Education in Chile, conducted by the Agency for Quality Education of the Ministry of Education in 2017. This database is based on the administration of a civic knowledge test to students and questionnaires to various members of the educational community. The target population consists of 8th-grade students in 242 schools across the country. Initially, the database comprises 8,589 student observations and 6,770 parent observations. However, considering the survey's unit of analysis and to ensure higher data quality, 171 student cases and 79 parent cases exhibiting repetitive and careless response patterns were removed (Gottfried et al., 2022). Additionally, data from the System for Measuring the Quality of Education (SIMCE) conducted by the Ministry of Education for the year 2017 are employed, providing school-level information such as administrative dependence, socioeconomic classification, and results obtained in standardized mathematics and language tests. After variable processing and removal of missing cases, the final database for this study includes a two-level stratified sample, composed of 5,047 students and parents (level 1) nested within 231 schools (level 2).

### Variables

@@

**Justification of Inequality**: The dependent variable in this study is the justification of social inequality in specific policy domains, namely health, education, and pensions. This construct is measured through three variables addressing the degree of justification regarding whether access to social services in these domains should be income conditional. Justification of inequality in health is measured by the item "Is it fair in Chile that people with higher incomes can access better healthcare than those with lower incomes," while in education, it is measured using the statement "Is it fair in Chile that people who can afford it have better education for their children." In the case of pensions, it is measured through the item "Is it fair in Chile that people with higher incomes can have better pensions than those with lower incomes." In all cases, respondents declare their preferences on a Likert scale ranging from "completely disagree" (1) to "completely agree" (4). Additionally, we include a summarized indicator of preferences for market justice (REF), measured by an average index across these items (α = 0.86), with values ranging from 1 to 4, where higher values represent greater preferences for market justice (see @tbl-desc-dependientes).

@@

The analysis includes several individual control variables that have been identified as influential in recent research. These variables encompass family socioeconomic status, assessed by the highest level of parental education, the number of books in the household, and an index measuring access to technologies, all aimed at mitigating compositional effects (REFS). @tbl-desc-independent shows the independent variables used, their response categories and their frequencies.

@@

This study examines four variables at the school level. Firstly, we assess the administrative dependence of schools, categorized as "Public," "Subsidized Private," or "Private." Secondly, we consider the socioeconomic classification of schools, determined by the Ministry of Education and measured on an ordinal scale with five categories ranging from "low" (1) to "high" (5). Thirdly, we evaluate the performance level of schools in SIMCE standardized tests, categorized as "low," "medium," or "high." Lastly, we analyze the proportion of parents with university or postgraduate education level at each school. The items used, response categories, and their frequencies are detailed in @tbl-desc-school.

@@

### Methods

>>>>

---
author: "Equipo Edumer"
editor: visual
---

# Data, variables and method

## Data

## 🗒️ Answer

The First Study of Civic Education in Chile, conducted by the Agency for Quality Education of the Ministry of Education in 2017, serves as the main data source. This database is composed by a civic knowledge test score and a series of items batteries measuring different aspects of citizenship. The target population includes 8th-grade students in 242 schools nationwide, as well as their parents and teachers. Initially, the database contains 8,589 student observations and 6,770 parent observations. To ensure higher data quality and considering the survey's unit of analysis, we removed 171 student cases and 79 parent cases that exhibited repetitive and careless response patterns (Gottfried et al., 2022). Additionally, we utilized data from the System for Measuring the Quality of Education (SIMCE) conducted by the Ministry of Education in 2017, which provides school-level information such as administrative dependence, socioeconomic classification, and results obtained in standardized mathematics and language tests. After processing the variables and removing missing cases, the final database for this study includes a two-level stratified sample composed of 5,047 students and parents (level 1) nested within 231 schools (level 2).

## Variables

@@

**Justification of Inequality**: The dependent variables in this study are market justice preferences. This construct is measured through three variables addressing the degree of justification regarding whether access to social services in pensions, education and health should be income conditional. Justification of inequality in health is measured by the item "Is it fair in Chile that people with higher incomes can access better healthcare than those with lower incomes,", and the same is asked for education and pensions. In all cases, respondents declare their preferences on a Likert scale ranging from "completely disagree" (1) to "completely agree" (4). Additionally, we include a summarized indicator of preferences for market justice (REF), measured by an average index across these items (α = 0.86), with values ranging from 1 to 4, where higher values represent greater preferences for market justice (see @tbl-desc-dependientes). We analyzed these items independently as well as by constructing and average index called "market justice preferences".

@@

The analysis includes several individual control variables that have been identified as influential in recent research. These variables encompass family socioeconomic status - by the highest level of parental education -, the number of books in the household, and an index measuring access to technologies. @tbl-desc-independent shows the independent variables used, their response categories and their frequencies.

@@

This study examines four variables at the school level. Firstly, we assess the administrative dependence of schools, categorized as "Public," "Subsidized Private," or "Private." Secondly, we consider the socioeconomic classification of schools, determined by the Ministry of Education and measured on an ordinal scale with five categories ranging from "low" (1) to "high" (5). Thirdly, we evaluate the performance level of schools in SIMCE standardized tests, categorized as "low," "medium," or "high". SIMCE (System of Measurement of Educational Quality) is a national test in areas such as language and mathematics which is applied yearly in different educational levels (REF). Lastly, we analyze the proportion of parents with university or postgraduate education level at each school. The variables, response categories, and their frequencies are detailed in @tbl-desc-school. {@kevin arreglar N L2 tabla}

@@

## Methods
